---
title: "msaWrapper_ordinalClass"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msaWrapper_ordinalClass}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(msaWrapper)
```

# Load tte data

Use the published patritumab trial data included in the package. This is tte data but ordinal class data has been created by splitting at the median survival time.

```{r}
data("oclass_data")
```

# Assign covariate groups

We can put the covariates into groups (eg from different modalities).

This must align with the 'data' we pass to msaWrapperCreate. 'Drug' will be the class, do not label this column. Also outcome will be ignored.

```{r}
names(oclass_data)
# Start at 2 after Drug column
groups <- c(rep(2,2), rep(3,6), 1, rep(2,3), rep(4,26), 5, 6, 6, rep(7, 3),
            rep(4,26), 6, 6, 5, rep(7, 3))
groupNames <- c("Drug", "Clinical", "Site", "immune", "FRET", "miR", "missing")
length(groups)
```

# Create msaWrapper object

```{r}
msa <- msaWrapperCreate(oclass_data[,2:77], oclass_data[,78],
                        group = groups, groupLabels = groupNames)
print(msa)
```

# Plot correlations

```{r}
plotDataCorrelations(msa, method = "pearson", textSize = 3)
```

And for only some groups.

```{r}
plotDataCorrelations(msa, method = "pearson", groups = c(4,5,6),
                     textSize = 4)
```

## Find strong correlations

```{r}
s <- strongDataCorrelations(msa, method = "pearson", threshold = 0.8)
print(s)
```

Plot some of them.

```{r}
plotStrongCorrelations(msa, s[1:2,], method = "pearson", trans = "log10")
```

# Plot selected cross correlations

```{r}
plotDataCrossCorrelations(msa,  method = "pearson", textSize = 5,
                          group1 = c(2,5,6), group2 = c(4))
```

# Plot outcome

```{r}
plotOutcome(msa)
```

# Plot outcome correlations

```{r}
msa <- generateOutcomeCorrelations(msa, method = "kendall")
plotOutcomeCorrelations(msa, groups = c(2,4,5,6))
```

```{r}
c <- as.factor(ifelse(msa$data$Sex, "female", "male"))  # this may not be right way around.
plotOutcomeByClass(msa, c, "Sex")
```

# Data Reduction

```{r}
reduced_msa <- reduceByCorrelationWithinGroups(msa, threshold = 0.6)
```

# Build Random Survival Forest

```{r, eval=FALSE}
# this will take some time
RSF <- buildRandomForest(reduced_msa, iterations = 10)
plotRandomForestPerformance(RSF)
print(RSF$optimal_covars)
```

```{r}
sessionInfo()
```
