---
title: "msaWrapper_ordinalClass"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msaWrapper_ordinalClass}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(msaWrapper)
```

# Load tte data

Use the published patritumab trial data included in the package. This is tte data but we can use one of the variables as an ordinal class for prediction.

```{r}
data("tte_data")
```

# Assign covariate groups

We can put the covariates into groups (eg from different modalities).

This must align with the 'data' we pass to msaWrapperCreate. 'Drug' will be the class, do not label this column. Also tte outcome will be ignored.

```{r}
names(tte_data)
# Start at 2 after Drug column
groups <- c(rep(2,2), rep(3,6), 1, rep(2,3), rep(4,26), 5, 6, 6, rep(7, 3),
            rep(4,26), 6, 6, 5, rep(7, 3))
groupNames <- c("Drug", "Clinical", "Site", "immune", "FRET", "miR", "missing")
length(groups)
```

# Create msaWrapper object

```{r}
msa <- msaWrapperCreate(tte_data[,2:77], tte_data[,1],
                        group = groups, groupLabels = groupNames)
summary(msa)
```

# Plot correlations

```{r}
plotDataCorrelations(msa, method = "pearson", textSize = 3)
```

And for only some groups.

```{r}
plotDataCorrelations(msa, method = "pearson", groups = c(4,5,6),
                     textSize = 4)
```

## Find strong correlations

```{r}
s <- strongDataCorrelations(msa, method = "pearson", threshold = 0.8)
print(s)
```

Plot some of them.

```{r}
plotStrongCorrelations(msa, s[1:2,], method = "pearson", trans = "log10")
```

# Plot selected cross correlations

```{r}
plotDataCrossCorrelations(msa,  method = "pearson", textSize = 5,
                          group1 = c(2,5,6), group2 = c(4))
```

# Plot outcome

```{r}
plotOutcome(msa)
```

```{r}
c <- as.factor(ifelse(msa$data$Sex, "female", "male"))  # this may not be right way around.
plotOutcomeByClass(msa, c, "Sex")
```

```{r}
sessionInfo()
```
