---
title: "msaWrapper_TimeToEvent"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msaWrapper_TimeToEvent}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(msaWrapper)
```

# Load tte data

Use the published patritumab trial data included in the package.

```{r}
data("tte_data")
```

# Assign covariate groups

We can put the covariates into groups (eg from different modalities). This must match the 'data' we pass to msaWrapperCreate, so do not label the outcomes.

```{r}
names(tte_data)
groups <- c(1, rep(2,2), rep(3,6), 1, rep(2,3), rep(4,26), 5, 6, 6, rep(7, 3),
            rep(4,26), 6, 6, 5, rep(7, 3))
groupNames <- c("Drug", "Clinical", "Site", "immune", "FRET", "miR", "missing")
length(groups)
```

# Create msaWrapper object

```{r}
msa <- msaWrapperCreate(tte_data[,1:77], tte_data[,78:79],
                        group = groups, groupLabels = groupNames)
print(msa)
```

# Plot correlations

```{r}
plotDataCorrelations(msa, method = "pearson", textSize = 3)
```

And for only some groups.

```{r}
plotDataCorrelations(msa, method = "pearson", groups = c(4,5,6),
                     textSize = 4)
```

## Find strong correlations

```{r}
s <- strongDataCorrelations(msa, method = "pearson", threshold = 0.8)
print(s)
```

Plot some of them.

```{r}
plotStrongCorrelations(msa, s[1:2,], method = "pearson", trans = "log10")
```

# Plot selected cross correlations

```{r}
plotDataCrossCorrelations(msa,  method = "pearson", textSize = 5,
                          group1 = c(2,5,6), group2 = c(4))
```

# Plot outcome

```{r}
plotOutcome(msa)
```

```{r}
c <- as.factor(ifelse(msa$data$Sex, "female", "male"))  # this may not be right way around.
plotOutcomeByClass(msa, c, "Sex")
```

# Plot outcome correlations

```{r}
msa <- generateOutcomeCorrelations(msa, method = "kendall")
plotOutcomeCorrelations(msa, groups = c(2,4,5,6))
```

# Data Reduction

```{r}
reduced_msa <- reduceByCorrelationWithinGroups(msa, threshold = 0.6)
```

# Build Random Survival Forest

```{r, eval=FALSE}
# this will take some time
RSF <- buildRandomForest(reduced_msa, iterations = 10)
```

```{r}
sessionInfo()
```
